Heritability

### 2022-09-14 R/02-process-herit.Rmd
update analyses and intermediate data files

>>>>

```{r}
offspring_each <- 
  offspring %>% 
  group_by(passage, treat) %>% 
  mutate(offspring = log_ch4)

heritability_each <- 
  selected_mean %>% 
  left_join(offspring_each, by = c("passage", "treat")) %>% 
  filter(passage != 5) %>% # Remove passage 5, which has no offspring
  ungroup()

write_tsv(heritability_each, paste0(der_dir, 'heritability_each.tsv'))

```

### 2022-09-14 R/04-heritability.Rmd
convert pngs to svgs for poster and update some figure details
update analyses and intermediate data files

p_herit <- plot_herit(heritability)

@@

ggsave('Manuscript/fig2.jpg', p_herit, width = 4, height = 3)

@@

>>>>

  ratio <- calc_plot_ratios(heritability$selected, heritability$offspring)
p_herit <- 
  ggplot(heritability, aes(selected, offspring, color = treat)) +
    geom_point() + 
    stat_smooth(method = 'lm', se = FALSE, formula = 'y ~ x') +
    labs(x = expression(Parental ~ log[10] ~ CH[4] ~ "(-k)"), 
         y = expression(atop(Offspring, log[10] ~ CH[4] ~ "(-k)"))) +
    scale_color_manual(name = "Treatment", 
                       labels = c('Neutral', 'Positive'), 
                       values = c('gray40', 'darkorange2')) +
    coord_fixed(ratio)

@@

ggsave('Manuscript/fig2.jpg', p_herit, width = 4, height = 3) 
ggsave('Manuscript/fig2.svg', p_herit, width = 4, height = 3)

@@

```{r}
heritability_each <- read_tsv(paste0(der_dir, 'heritability_each.tsv'))

fit_no_treat <- lm(offspring ~ selected, data = heritability_each)
kable(tidy(fit_no_treat))
herit_model <- lm(offspring ~ selected * treat, data = heritability_each)
kable(tidy(herit_model))
kable(tidy(anova(fit_no_treat, herit_model)))

ratio <- calc_plot_ratios(heritability_each$selected, heritability_each$offspring)
p_herit_each <- 
ggplot(heritability_each, aes(selected, offspring, color = treat)) +
    # theme_classic() +
    # geom_rangeframe(color = 'black') +
    geom_point() + 
    stat_smooth(method = 'lm', se = FALSE, formula = 'y ~ x') +
    labs(x = expression(atop(Mean ~ Parental, log[10] ~ CH[4] ~ "(-k)")), 
         y = expression(atop(Offspring, log[10] ~ CH[4] ~ "(-k)"))) +
    scale_color_manual(name = "Treatment", 
                       labels = c('Neutral', 'Positive'), 
                       values = c('gray40', 'darkorange2')) +
    coord_fixed(ratio)

save(p_herit_each, file = 'Output/herit_plot.RData')

ggsave('Manuscript/fig2_each.jpg', p_herit_each, width = 4, height = 3) 
ggsave('Manuscript/fig2_each.svg', p_herit_each, width = 4, height = 3) 
```
